Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-04-22 Paper/manuscript_v2/manuscript_07_01.tex
add details of the hyperparameters' prior distributions of sec 5.1

>>>>

The joint posterior parameter distributions are estimated from the sampling data using dynamic HMC algorithm implemented in Stan \citep{carpenter2017stan,betancourt2017conceptual}. A $\mathrm{Gamma}(1,1)$ prior distribution has been used for both observation noise $\sigma$ and covariance function marginal variance $\alpha$, and a $\mathrm{Gamma}(3.75,25)$ prior distribution for lengthscale $\ell$, either in exact GP or HSGP models.
